State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-10 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added notes for ken

There are two options available to alleviate problems with aliasing. The first, which is the most desirable, is to increase the spatial sampling frequency (using a higher resolution of sensors). The second is to use wider sensors, where the spatial averaging acts like a low-pass anti-aliasing filter. This option is a compromise between alleviating issues with aliasing and loosing high frequency information contained in the field. In practice, it is difficult  to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations. However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}. Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics. However, after applying the basis function decomposition, high frequency components contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}. This is further illustrated our results.

@@

The dynamic field must be spatially oversampled using a larger number of sensors then imposed by frequency analysis considerations, to use frequency analysis to determine the minimum distance and width of the basis functions. Following this, the distance between basis functions is usually larger then the distance between sensors, although this is not a requirement for using this estimation framework. For a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid. Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.

>>>>

There are two options available to alleviate problems with aliasing. The first, which is the most desirable, is to increase the spatial sampling frequency (using a higher resolution of sensors). The second is to use wider sensors, where the spatial averaging acts like a low-pass anti-aliasing filter. This option is a compromise between alleviating issues with aliasing and loosing high frequency information contained in the field. In practice, it is difficult  to estimate the bandwidth of the cortex using traditional electrophysiological measurements due to spatial limitations. However, we envisage it may be possible the estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}. Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics. However, after applying the basis function decomposition, high frequency components contribute negligibly to the inverse problem and are therefore not a major problem for the state and parameter estimation~\cite{Sanner1992}. This is further illustrated our results. \omg{Although our results are severely effected by the loss of high frequency info! Ken: Do you think you can word this a little better than what I have done.}

@@

The dynamic field must be spatially oversampled using a larger number of sensors then imposed by frequency analysis considerations, to use frequency analysis to determine the minimum distance and width of the basis functions. Following this, the distance between basis functions is usually larger then the distance between sensors, although this is not a requirement for using this estimation framework. \omg{Ken: can you please write something about what should be done in this case?} For a spatially homogeneous isotropic fields, the basis functions can be placed on a regular grid. Following this, the knowledge of the distance between basis functions directly implies the total number of basis functions required.
